Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-17 manuscript.tex
minor updates

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{(left) Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 3\% facula on the simulated Sun. (right) Correlations between the different width parameters and their corresponding RV estimates for the same facula.
   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations for all the cases but the correlation between N mean RV and BIS SPAN (p--values=0.39).
   }
    \label{fig:faculae.corr}
\end{center}
\end{figure*}

@@

Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can also help to better probe stellar rotational periods or to better understand the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}. 
We saw that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
%\xavier{This is of course a problem for photon-noise limited observations.} 
However, when looking at bright
stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have significant impact
on the RV precision as the instrumental noise will dominate the data. 
Therefore, for bright targets, stellar activity 
can be better characterized by using SN mean RV as this RV estimate is more sensitive to it.
%
%This is not necessarily a negative aspect. 
%For example, in the case where photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
%\jessi{I'm not sure I agree with the previous statements - more uncertainty means you would be less certain if the RV estimate is due to actual stellar activity or just photon noise.  It is also stated throughout that precise estimates are needed (e.g. in the conclusion)}
%\umberto{Xavier, can you please develop a little bit this statement? If I understood correctly, since the correlation between the width and the asymmetry of the CCF with SN mean RV is almost always the strongest, if the star is particularly active we are willing to ``sacrifice'' the precision of the RV if we can end up with a clear indication of strong activity by the star. Is it correct?}

>>>>

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{(left) Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 3\% facula on the simulated Sun. (right) Correlations between the different width parameters and their corresponding RV estimates for the same facula.
   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations for all the cases except for the correlation between N mean RV and BIS SPAN (P-value = 0.39).
   }
    \label{fig:faculae.corr}
\end{center}
\end{figure*}

@@

Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can also help to better probe stellar rotational periods or to better understand the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}. 
We saw that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
%\xavier{This is of course a problem for photon-noise limited observations.} 
However, when looking at bright
stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have a significant impact
on the RV precision as the instrumental noise will dominate the data. 
Therefore, for bright targets, stellar activity 
can be better characterized by using SN mean RV as this RV estimate is more sensitive to it.
%
%This is not necessarily a negative aspect. 
%For example, in the case where photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
%\jessi{I'm not sure I agree with the previous statements - more uncertainty means you would be less certain if the RV estimate is due to actual stellar activity or just photon noise.  It is also stated throughout that precise estimates are needed (e.g. in the conclusion)}
%\umberto{Xavier, can you please develop a little bit this statement? If I understood correctly, since the correlation between the width and the asymmetry of the CCF with SN mean RV is almost always the strongest, if the star is particularly active we are willing to ``sacrifice'' the precision of the RV if we can end up with a clear indication of strong activity by the star. Is it correct?}
